\BeginJob{Raytheon Technologies}{August 2021}{Nov 2021}{Senior Principal Software Engineer}{Remote: Golden, CO}
    \WorkItem{Digital Transformation - Digital Thread Product Owner}
        \begin{itemize}
            \item Responsible for digital thread roll-out to multiple path finder programs.
            \item Prioritized, budgeted and tracked multiple teams delivering digital thread capability to multiple programs.
            \item Managed research and development budget >\$ 4M per year.
        \end{itemize}
    \WorkItem{MissileKit Embedded Software Product Owner}
        \begin{itemize}
            \item Planned and provided embedded software capabilities for MissileKit common product.
            \item Modernized MissileKit product to align with modern container based development and test strategies.
        \end{itemize}
    \WorkItem{Program Mentorship}
        \begin{itemize}
            \item Provided training and guidance for first time software development leads.
            \item Provided technical guidance on software architecture and testing practices.
        \end{itemize}

\EndJob
\BeginJob{Raytheon Technologies}{January 2019}{August 2021}{Principal Software Engineer}{Tucson, AZ / Remote: Golden, CO}
\WorkItem{Digital Transformation - Digital Thread Product Owner}
    \begin{itemize}
        \item Evaluated multiple software products that generate digital threads via data linking and data synchronization.
        \item Worked with digital thread tooling vendor, SBE Vision, to deploy data synchronization platform connecting multiple commercial and internally developed tools creating a model-based digital thread. (NDIA presentation pending)
    \end{itemize}
\WorkItem{MissileKit Embedded Software Technical Authority}
    \begin{itemize}
        \item Mentored a cross-disciplinary team on software architecture, code quality, DevSecOps, and algorithm performance.
        \item Extended common software build system to support cross-compilation for VxWorks operating system.
        \item Integrated Quick Emulator (QEMU) based testing system integrating 6-DOF simulator with software compiled for embedded processors.
    \end{itemize}
\WorkItem{Advanced programs software Product Area Lead (PAL)}
    \begin{itemize} 
        \item Software technical authority for advanced programs product line. Responsible for software execution of a large portfolio of research and development programs.
        \item Provided programs with software design, cost estimation, debugging, and integration support.
        \item Mentored multiple early-career engineers in advanced programs product line. Focus on topics such as software development and missile technology.
    \end{itemize}
\EndJob
\BeginJob{Raytheon Technologies}{January 2017}{December 2018}{Senior Engineer II}{Tucson, AZ}
\WorkItem{Missile Systems Innovation Center Lead}
    \begin{itemize}
            \item Lead large cross-functional team reporting directly to Vice President of Engineering.
            \item Managed a yearly budget > \$1M.
            \item Executed of yearly Missile Systems Hackathon, a 2 Day open format event.
            \item Provided access to open use maker spaces which include 3d-printers and electronics kits.
            \item Worked with Spigit innovation management software to launch Igniter, Raytheon's web-based innovation challenge platform.
            \item Executed 30+ Igniter challenges in CY2019.
    \end{itemize}
    \WorkItem{\bf{Recognition:} Technical Honors, Raytheon Missile Systems President's Award}
\EndJob
\BeginJob{Raytheon Technologies}{August 2012}{December 2017}{Senior Software Engineer }{Tucson, AZ}
\WorkItem{Phaser}
    \begin{itemize}
        \item Lead developer for Phaser GPS spoofing payload extending NavSats payload to multiple signals and spoofing mission.
        \item Verified spoofing performance against 3rd party GPS receiver.
        \item Demonstrated spoofing performance to multiple DOD customers.
    \end{itemize}
\WorkItem{NavSats}
    \begin{itemize}
        \item Lead developer for NavSats payload integrating Chip Scale Atomic Clock (CSAC) with Xilinx SOC to create a precision timed reconfigurable software-defined radio.
        \item Developed payload embedded software and configurable logic responsible for generating representative GPS signal.
        \item Integrated payload with hardware in the loop testbed created with STK and RF channel simulator for performance testing.
        \item Leveraged auto-generation of code and configurable logic via Xilinx System Generator and Simulink.
    \end{itemize}
\WorkItem{Evolved Sea Sparrow Missile}
    \begin{itemize}
        \item Scrum master for radar modes team. Worked with product owner to plan and execute multi-year backlog.
        \item Integration of high fidelity radar signal simulator with 6-DOF physics simulation.
        \item Certified Scaled Agile Framework (SAFe) scrum master and product owner. 
    \end{itemize}
\WorkItem{Low cost active seeker}
    \begin{itemize}
        \item Developed and integrated active radar exciter receiver system.
        \item Implemented radar dwell scheduling algorithm for minimization of eclipsing.
        \item Implemented DevOps/CI based documentation process to automatically generate customer compliant test documentation.
    \end{itemize}
\WorkItem{Acellerated Improved Interceptor Initiative}
    \begin{itemize}
    \item Developed and integrated driver for semi-active radar.
    \item Supported field testing against live targets.  
    \item Implemented DevOps/CI testing for rapid release and deployment of embedded software.
    \end{itemize}
\WorkItem{\bf{Recognition:} Technical Honors, leadership development program graduate, SWIFT innovator of the year } 
\EndJob


\BeginJob{Raytheon Technologies}{April 2012}{August 2012}{Software Engineer II}{Tucson, AZ}
    \WorkItem{Embedded software engineer AI3 missile defense program.  }
    \WorkItem{Developed and integrated device drivers for inertial measurement unit and communication system.}
\EndJob
